Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-07-01 extended_catalog/paper/extended_catalog.tex
typos

@@

\pointlike uses the \minuit fitting library to simultaneously maximize
the likelihood by fitting the position and extension of an extended
source (\cite{minuit_documentation}).  For each position and extension,
the spectral parameters of the sky model are refit. To avoid projection
effects, what is directly fit is not the longitude and latitude of
the source but instead the displacement in a rotated reference frame.
The significance of the extension of a source can be calculated from
\tsext, which is defined as twice the increase in log likelihood between
the extended source model at its best fit values and the
point source model at its best fit values:
\begin{equation}
  \tsext=2\times(LL_\text{ext}-LL_\text{ps}).
\end{equation}
The interpretation of \tsext in terms of a statistical significance is
discussed in section~\ref{significance_of_extension}.

@@

An extended source must be modeled by an assumed spatial shape and
the convolution of that shape with the PSF is fit to the data.
Possible choices for spatial models include a two dimensional Gaussian
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk:
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(\sqrt{x^2+y^2}<\sigma\right).
\end{equation}
Although these shapes are significantly different from each other, the
convolution of these spatial models of typical sizes with the PSF will
produce PDFs that are very similar.

This is demonstrated in figure~\ref{compare_disk_gauss}.  The plot shows
(in black) the PSF that would be observed for a source of spectral
index 2. The dashed red (blue) line shows the probability density
function for a Gaussian (uniform disk) of width $0.5\deg$.  The solid
red (blue) line shows the probability density function for the same
Gaussian (uniform disk) convolved with the PSF of an index 2 source.
Figure~\ref{compare_disk_gauss} shows the analysis using an energy range
between 1 \gev and 100 \gev whereas the right plot shows an analysis using an
energy range from 10 \gev to 100 \gev.

This plot shows that significantly different extended source shapes
look very similar after smearing with the PSF. The convolved shape of
the disk and Gaussian admittedly do look more different when restrict
ourselves to higher energy where the PSF is narrower, but we do not
except to have much luck learning about the exact nature of the
extended source shape. For that reason, in this paper we always use
the uniform disk spatial model to emphasize our ignorance to the true
shape of the extended sources we are studying.

To get the convolved disk and Gaussian models looked so similar in
figure~\ref{compare_disk_gauss}, we had to pick the extension of the two
sources so that they each predicted a 68\% containment radius of 0.5\deg.

The 68\% containment radius for a spatial model is
the radius at which 68\% of the intensity is enclosed.
It can be computed by a straightforward integral and we
find that $\rsixeight_\text{,disk}=0.82\sigma$ whereas
the $\rsixeight_\text{,Gaussian}=1.51\sigma$. Therefore, in
figure~\ref{compare_disk_gauss} the uniform disk has an extension
of $\sigma=0.41\deg$ whereas the Gaussian has an extension of
$\sigma=0.75\deg$. Even though these sources have quite different
values of the extension $\sigma$, they look almost identical when convolved
with the PSF.

Finally, we note that comparing observed morphologies to 
counts maps can be misleading.  This effect can best be seen
in figure~\ref{compare_r68} where we have simulated a
extended source with 
a spatial model that is a uniform disk of extension 0.5\deg,
integral flux between 1 \gev and 100 \gev of $3e-8\ph/\cm^2/s$,
and a spectral index of 2.

To reduce Poisson noise, figure~\ref{compare_r68} shows a counts map of
this simulated source smoothed with a 0.1\deg Gaussian kernel. Overlaid
on the plot is the results of fitting this simulated source with a uniform
disk and a Gaussian spatial model.  The solid white line represents the
fit extension $\sigma_\text{disk}=0.496$ for the disk which was found to
be in very good agreement with the simulated value.  The solid black line
represents the fit extension $\sigma$ for the Gaussian which was found to
be $\sigma_\text{Gaussian}=0.2627$.  The white dashed line is the 68\%
containment radius of the fit Disk shape and the black dashed line is
the 68\% containment radius of the fit Gaussian shape.  Even though the
fit $\sigma$ for the disk and uniform Gaussian are different, the fit
68\% containment radius are very similar ($\rsixeight_\text{,disk}=0.41$
whereas $\rsixeight_\text{,Gaussian}=0.40$).

There are three important conclusions to take from this. The first is
that depending upon what spatial model you pick and what parameter you
choose to overlay on the smoothed counts ($\sigma$ or $rsixeight$),
you will get very different looking shapes even though the all lead
to a PDF which is very similar. And since we are not very sensitive
to the particular morphology of extended sources that we are seeing,
there is no correct choice for which shape to use. For the following
analysis, we always use a uniform disk as our spatial model because
of its conceptual simplicity and to emphasize our ignorance to the
true morphology. And for subsequent smoothed counts maps, we overlay
the $\sigma$ because that shows directly the edge of the shape we fit.
But due to smearing of the PSF, it has the unfotunatly concequence that
the extended source shape always (including in the simulated image)
looks larger than in the counts map.

The second conclusion we make is that because a counts map is smeared
out by the PSF and depends strongly on the particular color bar used, it
is very difficult to determine directly from a counts map a reasonable
spatial model that fits the data.  It is much better to obtain the
spatial model by a direct fit of a spatial parameters of a selected
model to the data.  The third conclusion we make is that when comparing
fit extensions to those at other wavelenghts (especially in \tev), it is
important to compare fits of consistent spatial models. If this is not
possible, it is impotant to at least compare indirectly the $rsixeight$
for the different spatial models.

@@

\subsection{Significance of Extension}
\label{significance_of_extension}

The value of \tsext, the increase in likelihood fitting the source
with an extended spatial model, can be used to calculate
the statistical significance of the source's extension.
Since the point and extended models are nested hypothesis,
we would always expect $\tsext>0$.

We would expect that if we were really testing a point source that
\tsext would not be very large since a point model would fit about
as good as anytthing else. Therefore, we can consider a source to be
extended (and reject the null hyopthesis) if \tsext is large enough.
Since going from fitting a point soue to fitting a simple extended
source introduces only one degree of freedom (the source's extension)
Wilks' Theorem says that the distribution of $\tsext$ wen testin
point sources should follow a $\chi^2_1$ distribution with one degree
of freedom (\cite{wilks_theorem}).

On the other hand, since the null hypothesis rests on the edge of
parameter space, when the extension is fixed to 0, Wilks' Theorem does
not formally hold (\cite{warn_wilks_theorem}).  One might
expect the actual distribution to be a half $\chi^2_1$ distribution with
one degree of freedom plus half of a delta function at 0:
\begin{equation}
  P(\ts)=\tfrac{1}{2}(\chi^2_1(\ts)+\delta(\ts)).
\end{equation}
Chernoff proved that given certain assumtipons, this is
the ditribution that would hold when the null hypothesis
lies on the edge of parameter space for a particular parameter~\ref{chernof}.
The false detection probability can be estimated by integrating this function 
from an observed test statistic value to infinity. It is for this
particular distribution that the often quoted result holds that
$\sqrt{\ts}$ is a measure of the number of $\sigma$ of the detection.

It should be noted that Wilks' Theorem only holds when the likelihood
is maximized simultaneoulsy fitting all of the parameters of model. It
is for this reason why \pointlike goes through such great effort to
simultaneously fit the position, extension, and spectral paramters of
a source.

The half $\chi^2_1$ distribution was found by a Monte Carlo study
to hold for the special case of source finding of EGRET sources using the
maximum likelihood technique.  They were comparing the hypothesis of a
source to the hypothesis of just a background (\cite{mattox_egret}).
Their argument for why this null hypothesis distribution was reasonable
was that half of the time, statistical underfluctuations would cause
there to be fewer fewer photons then expected where the sources is being
tested. Since the maximim likelihood machinery cannot fit negative
sources (which would lead to negative model predicted for which the
poisson likelihood is undefined), half of the tests would not have the
likelihood improved by adding a source to the model and $\ts=0$.
It is for the case that the null distribution has

It seems plausable that a similar situation could happen when testing
a source for extension. Half of the time, statistical flucutations might
make the observed counts narrower thant the point spread function and
the likelhood would not improve by fitting the source with an extended
hypothesis. We tested this hypothesis below using a dedicated monte
carlo study.

One issue that we found when testing this analysis method is that
despite our best efforts, there was always a small discrepancy between
the likelihood value when fitting the source as a point source and when
fitting it as an extended source with a small extension.  This is to be
expected due to numerical innacuracies introduced by the convolution.
For most cases, this error is insignificant. It would not significanlty
bias any of the fit values or errors. But it would bias the distribution
of $\tsext$ in the null hypothesis. To correct for this,
instead of computing the likelihood in the null hypothesis by fitting
a point source, a new source model was introduced which is an extended
source with its extension fixed to a very small value. $LL_\text{ps}$
is then calculated by refitting this source using the same extended
source fitting code. It was only after introducing this change that we
were able to get broad agreement between simulations and Wilks' theorem.

\subsection{Monte Carlo Validation} \label{monte_carlo_validation}

We performed a dedicated Monte Carlo study to validate \pointlike for
studying spatially extended sources and also to demonstrate that we can
use $\tsext$ as a test of the statistical significance
of a source's extension.  The Monte Carlo study involved simulating point
sources of varying spectral models on top of a simulated background. The
simulated point source was then fit using \pointlike as both an extended
source and a point source and $\tsext$ was calculated.

Fermi LAT data was simulated using program 
\gtobssim\footnote{\gtobssim is distributed by and supported 
by the Fermi Science Support Center
(\cite{fssc}).}  The sources were simulated with a powerlaw spectral
model with 6 Were given 6 $>100$ \mev fluxes ranging from $3\times 10^{-9}
\ph/\cm^2/s$ to $10^{-6} \ph/\cm^2/s$.  The sources were then simulated
with spectral index ($\gamma$) values of 1.5, 2, 2.5, and 3.  These
values were picked to probe a representative range measurable values.
For particular spectral indices, only the fluxes which would create a
statistically significant source detection ($\ts>25$) where selected,
since we are only interested in testing for extension sources with a
significant extent. The sources were simulated on top of an isotropic
powerlaw background with a Sreekumar-like spectrum ($>100$ \mev flux
of 1.5e-5 and spectral index 2.1) (\cite{sreekumar_isotropic}).

@@

For most of the spectral models, over 10,000 statistically independent simulations were performed.
For fainter sources, some of the simulated sources, statistical fluctuations
caused the source to be not significant and they were excluded from the following analysis.
Table~\ref{ts_ext_num_sims} shows the parameters used in the simulation,
the number of simulations performed, and the average test statistic value.

The results of the Monte Carlo simulation are shown in
figure~\ref{ts_ext_mc}.  The cumulative density function (CDF) is plotted
against $\tsext$ For reference, the CDF for $\chi^2_1/2$,
suggested by Wilks' Theorem, is also plotted for comparison. Overall,
there is good agreement between Wilks' theorem, although the agreement is
not perfect.  It should be noted that the discrepancy seems to be worst
for bright sources which seems to imply that numerical errors in the
way \pointlike models the PSF and performs the convolution become more
apparent for sufficiently bright sources.  Other possible reasons for
departure from Wilks' theorem might include \pointlike ignoring energy
dispersion. Energy dispersion will change the shape as a function of
energy. \pointlike may also run into possibly problems with the fitting
algorithm getting stuck in false minimum. It is important to emphasize
that if
our emperical curve lies to the left of the curve we assume to estimate
significance, we would underestimate the statistical significance of
our result. Since this is the case for most of our simluations, we are
reasonable confident that $\sqrt{\tsext}$ can be safely
used as a measure of the statistical significance of a source's extension.

@@

We validated our method by testing for extension all of the sources
which the Fermi Collaboration had previously published on.  
This list includes the extended sources where were modeled
in the 2FGL catalog\cite{second_cat}.
This list contains the Large Magelenic Cloud and the Small Magilenic Cloud
which were first published in \cite{lmc,smc}.
We also included the Supernova rememants IC443, W28, W30,
W44, W51C, and the Cygnus Loop which were 
first published in \cite{ic443,w28,w30,w44,w51c,cygnus_loop}.
We include the Pulsar Wind Nebulae Vela X, MSH 15-52, and 
HESS J1825-137\cite{velax,msh1552,fermi_hess_j1825}.
In addition to those sources included by the catalog, we include in
this list the supernova rememnat RX J1713.7-3946 which was recently
published (\cite{RXJ1713}).

@@

  \begin{figure}
    \begin{center}
      \includegraphics{mc_plots/compare_disk_gauss.pdf}
      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
    \end{center}
    \caption{Comparison of Disk and Gauss.
    \todo[inline]{Add Caption.
    the overall point here is that disk looks like gauss once convolved with the psf.
    }
    }\label{compare_disk_gauss}
  \end{figure}

>>>>

% TODO:
%  how to format powerlaw, power-law, power law?

@@

\pointlike uses the \minuit fitting library to simultaneously maximize
the likelihood by fitting the position and extension of an extended
source (\cite{minuit_documentation}).  As will be described in
section~\ref{monte_carlo_validation}, the statistical significance
of the detection of an extended source can only be correctly calculated
when all of the parameters of a model are simultaneously fit

For each position and extension,
the spectral parameters of the sky model are refit. To avoid projection
effects, what is directly fit is not the longitude and latitude of
the source but instead the displacement in a rotated reference frame.
The significance of the extension of a source can be calculated from
\tsext, which is defined as twice the increase in log likelihood between
the extended source model at its best fit values and the
point source model at its best fit values:
\begin{equation}
  \tsext=2\log(LL_\text{ext}/LL_\text{ps}).
\end{equation}
The interpretation of \tsext in terms of a statistical significance is
discussed in section~\ref{monte_carlo_validation}.

@@

An extended source must be modeled with a spatial shape.
The convolution of that shape with the PSF is fit to the data.
Possible choices for spatial models include a two dimensional Gaussian
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{2\pi\sigma^2}\exp\left(-(x^2+y^2)/2\sigma^2\right)
\end{equation}
or a uniform disk
\begin{equation}
  \text{PDF}(x,y)=\tfrac{1}{\pi\sigma^2}\delta\left(x^2+y^2<\sigma^2\right).
\end{equation}
Although these shapes are significantly different, the
convolution of them with the PSF for typical sizes look very
similar.

This is demonstrated in figure~\ref{compare_disk_gauss}.  It shows the
PSF that would be observed for a powerlaw source of spectral index two,
the probability density function for a Gaussian and uniform disk of width
$0.5\deg$, and the probability density function for the same Gaussian
and uniform disk convolved with the PSF.  The figure shows the analysis
using an energy range between 1 \gev and 100 \gev and using an energy
range between 10 \gev and 100 \gev.  The convolved shape of the disk and
Gaussian do separate better at higher energy where the PSF is narrower.
This plot shows that the LAT is not very sensitive to probing different
kinds of extended sources.  In this paper we always fit with uniform disk
spatial models.

To get the convolved disk and Gaussian shapes to match in
figure~\ref{compare_disk_gauss}, we had to set them to predict
a 68\% containment radius of 0.5\deg.  The 68\% containment
radius for a spatial model is the radius at which 68\% of the
intensity is enclosed.  It can be computed by a straightforward
integral and we find that $\rsixeight_\text{,disk}=0.82\sigma$
whereas the $\rsixeight_\text{,Gaussian}=1.51\sigma$. Therefore, in
figure~\ref{compare_disk_gauss} the uniform disk has
$\sigma=0.41\deg$ whereas the Gaussian has 
$\sigma=0.75\deg$.

Finally, we note that comparing fit sizes to counts maps can look
misleading.  This effect can best be seen in figure~\ref{compare_r68}
which shows a simulated a extended source with a uniform disk spatial
model with $\sigma=0.5\deg$. The simulated source has integral flux
between 1 \gev and 100 \gev of $3\times 10^{-8}\ph/\cm^2/s$, and a
spectral index of 2.  To reduce Poisson noise, figure~\ref{compare_r68}
shows a counts map of this source smoothed with by a 0.1\deg Gaussian
kernel. Overlaid on the plot is the results of fitting this simulated
source with a uniform disk and a Gaussian spatial model.  The solid white
line represents the best fit disk extension $\sigma_\text{disk}=0.496$
The solid black line represents the fit extension $\sigma$ for the
Gaussian which was found to be $\sigma_\text{Gaussian}=0.2627$.
The white and black dashed lines are the 68\% containment radius of
the fit Disk and Gaussian respectivly.  Even though the fit $\sigma$
for the disk and uniform Gaussian seem very different, the fit 68\%
containment radius are very similar ($\rsixeight_\text{,disk}=0.41$
whereas $\rsixeight_\text{,Gaussian}=0.40$) and the results are in
agreement.

This study shows that depending upon what spatial model you pick and
what parameter you choose to overlay on the smoothed counts ($\sigma$ or
$rsixeight$), you will get shapes that look very different but predict
very similar counts distributions.  Since we are not very sensitive to
the particular morphology of an extended source, there is no correct
choice for which shape to use. For the following analysis, we always use
a uniform disk as our spatial model because of its conceptual simplicity
and to emphasize our ignorance to the true morphology. And for subsequent
smoothed counts maps, we overlay the $\sigma$ because that shows directly
the edge of the shape we fit.  But due to smearing of the PSF, it has the
unfortunate consequence that the extended source shape always (including
in the simulated image) looks larger than in the counts map.

The second conclusion we make is that because a counts map is smeared
out by the PSF and depends strongly on the particular color bar used, it
is very difficult to determine directly from a counts map a reasonable
spatial model that fits the data.  It is much better to obtain the
spatial model by a direct fit of a spatial parameters of a selected
model to the data.  The third conclusion we make is that when comparing
fit extensions to those at other wavelenghts (especially in \tev), it is
important to compare fits of consistent spatial models. If this is not
possible, it is important to at least compare indirectly the $rsixeight$
for the different spatial models.

@@

\subsection{Significance of Extension}
\label{monte_carlo_validation}

\tsext can be used to calculate the statistical significance
of the source's extension.  Since the point and extended models are
nested, we would always expect $\tsext>0$.  On the other hand,
we would not expect the likelihood to change very much unless the source
was significantly extended.  Since an extended source has one additional
degree of freedom, Wilks' Theorem says that the distribution
of $\tsext$ when testing a point source for extension should follow a
$\chi^2_1$ distribution (\cite{wilks_theorem}).

On the other hand, since the null hypothesis rests on the edge of
parameter space when the extension is 0, Wilks' Theorem does not hold
(\cite{warn_wilks_theorem}).  One might expect the actual distribution
to be a half $\chi^2_1$ distribution with one degree of freedom plus
half a delta function at 0:
\begin{equation}
  P(\ts)=\tfrac{1}{2}(\chi^2_1(\ts)+\delta(\ts)).
\end{equation}
Chernoff proved that under certain assumptions, this is the distribution
that would hold when the null hypothesis lies on the edge of parameter
space (\cite{chernof}).  The false detection
probability can be estimated by integrating this function from an observed
test statistic value to infinity. It is for this particular distribution
that the often quoted result holds that $\sqrt{\ts}$ is a measure of
the number of $\sigma$ of the detection (\cite{mattox_egret}).

The half $\chi^2_1$ distribution was found by a Monte Carlo study to hold
for the special case of source finding of EGRET sources using a maximum
likelihood analysis (\cite{mattox_egret}).  For half of the tests of a
point source, statistical fluctuations would make the observed counts look
narrower than the point spread function leading to $\tsext=0$. So it is
reasonable to expect that a similar half $\chi^2_1$ would be appropriate
for extension testing. We tested this hypothesis using a dedicated Monte
Carlo study.

Before we show the Monte Carlo simulations, we have to bring up one issue
we found with these tests.  Despite our best efforts, there was always
a small numerical discrepancy between the likelihood when fitting the
source as the PSF and when fitting it as a very small extended source
with This is due to numerical error introduced by the convolution.
In most situations, this error would be insignificant. But it does bias the
distribution of \tsext in the null hypothesis. To correct for this,
instead of computing the likelihood in the null hypothesis by fitting
the PSF, we instead fit the null hypothesis as an extended source with
the extension fixed to be very small.

The Monte Carlo study involved simulating point sources of varying
spectral models and fitting them using \pointlike as both point
and extended sources.  Fermi LAT data was simulated using program
\gtobssim\footnote{\gtobssim is distributed by and supported by the
Fermi Science Support Center (\cite{fssc}).}  The sources were simulated
with a powerlaw spectral model with 6 Were given 6 $>100$ \mev fluxes
ranging from $3\times 10^{-9} \ph/\cm^2/s$ to $10^{-6} \ph/\cm^2/s$.
The sources were then simulated with spectral index ($\gamma$) values of
1.5, 2, 2.5, and 3.  These values were picked to probe a representative
range measurable values.  For particular spectral indices, only the fluxes
which would create a statistically significant source detection ($\ts>25$)
where selected, since we are only interested in testing for extension
sources with a significant extent. The sources were simulated on top of
an isotropic powerlaw background with a Sreekumar-like spectrum ($>100$
\mev flux of 1.5e-5 and spectral index 2.1) (\cite{sreekumar_isotropic}).

@@

For most of the spectral models, over 10,000 statistically independent
simulations were performed.  For fainter sources, some of the
simulated sources, statistical fluctuations caused the source
to be not significant and they were excluded from the following
analysis.  Table~\ref{ts_ext_num_sims} shows the parameters used in
the simulation, the number of simulations performed, and the average
test statistic value.  The results of the Monte Carlo simulation are
shown in figure~\ref{ts_ext_mc}.  The cumulative density function (CDF)
is plotted against $\tsext$ For reference, the CDF for $\chi^2_1/2$,
suggested by Wilks' Theorem, is also plotted for comparison.

Our Monte Carlo study showed broad agreement between simulations and
Wilks' theorem and that we can use \tsext as a test of the statistical
significance of a source's extension.  Nevertheless, the agreement
is not perfect.  It should be noted that the discrepancy seems to be
worst for bright sources. This seems to imply that numerical errors in
the convolution become more apparent for sufficiently bright sources.
Other possible reasons for departure from Wilks' theorem might include
\pointlike ignoring energy dispersion. Energy dispersion will change
the shape as a function of energy. \pointlike may also run into possibly
problems with the fitting algorithm getting stuck in false minimum. It
is important to emphasize that if our emperical curve lies to the left of
the curve we assume to estimate significance, we would underestimate the
statistical significance of our result. Since this is the case for most
of our simluations, we are reasonable confident that $\sqrt{\tsext}$
can be safely used as a measure of the statistical significance of a
source's extension.

@@

We validated our method by testing for extension all of the sources
which the Fermi Collaboration had previously published on.  This list
includes the extended sources where were modeled in the two year catalog
(\cite{second_cat}).  This list contains the Large Magalenic Cloud
and the Small Magalenic Cloud which were previously published by the
LAT collaboration (\cite{lmc,smc}).  We also included the SNRs IC443, W28, W30, W44, W51C, and the Cygnus Loop which
were first published in \cite{ic443,w28,w30,w44,w51c,cygnus_loop}.
We include the Pulsar Wind Nebulae Vela X, MSH 15-52, and HESS
J1825-137\cite{velax,msh1552,fermi_hess_j1825}.  In addition to those
sources included by the catalog, we include in this list the SNR RX J1713.7-3946 which was recently published (\cite{RXJ1713}).

@@

  \begin{figure}
    \begin{center}
      \includegraphics{mc_plots/compare_disk_gauss.pdf}
      % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/compare_disk_gauss/v2/compare_disk_gauss.pdf
    \end{center}
    \caption{
    This plot demonstrates that different spatial models when smoothed
    out by the PSF look very similar.  The $y$ axis is the log of the
    intensity and the $x$ axis is $\theta^2$.  The black line are PSF that
    would be observed for a powerlaw source of spectral index two. The
    dashed red line is the probability density of a Gaussian of width
    $\rsixeight=0.5\deg$, which is a straight line in this log intensity
    vs $\theta^2$ plot.  The dashed blue line is the probability density
    for a uniform disk of $\rsixeight=0.5\deg$.  Finally, the solid red
    and blue lines show the convolution of the Gaussian and uniform disk
    with the PSF.  The left plot shows the analysis with an energy range
    from 1 \gev to 100 \gev whereas the right plot shows the analysis
    with an energy range from 10 \gev to 100 \gev.
    }\label{compare_disk_gauss}
  \end{figure}
